### 2021-02-18 notes/notes.tex
Redefined error clamp

\begin{chapter}{Glossary}
\begin{enumerate}
\item Error-clamp: Refers to the phase of a simulation in the models of motor adaptation where the error that drives learning is set to zero. This emulates a no-feedback experimental condition.
\end{enumerate}
\end{chapter}

@@

>>>>

\begin{chapter}{Glossary}
\begin{enumerate}
\item Error-clamp: Refers to the phase of a simulation in the models of motor
adaptation where the error that drives learning is forced to zero. For example,
when performing a task in which a robotic attachment creates forces perpendicular
to the direction of movement, an error-clamp phase is one in which the attachment
pushes the arm constantly towards the desired trajectory, thus making error zero.
\end{enumerate}
\end{chapter}

@@

Spontaneous recovery. In an A-B-error_clamp paradigm, in which during B the
opposite adaptation to A is learned, at the beginning of the error-clamp phase
(after B) participants seem to quickly gravitate towards A (thinking that A is
now active?). This would be displayed by the model via the state inference, as
now the visual cue and the observed dynamics point to different contexts. In
time, updating $p(context | visual cue)$ will lead to spontaneous recovery.
